Downward shortwave solar irradiance enhancement by clouds.

### 2024-05-23 article/article.Rmd
Commit 2024-05-23 10:10

@@

To give a better understanding of the CE identification procedure, we included 
an example of the CE identification for a selected day .... appendix....
where the use of the reference and the threshold are shown, along with the relevant
measurements.

Similar we provide yearly plots

- Include Example of days plot in the Appendix!
... this is clearer to understand and describe ....

@@

Our dataset, after the data selection processing, consists of
`r ST_total$wattGLB.N` records of GHI, of which
$`r round(100*ST_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ are CE and
$`r round(100*ST_extreme_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ are ECE events.
The highest GHI recorder was 
$`r round(ST_daily[which.max(wattGLB.max), wattGLB.max],1)`\,W/m^2$
on `r strftime(ST_daily[which.max(wattGLB.max), Date], "%d\\ %B %Y")`.
The absolute stronger CE event had an OIR of 
$`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 2)`\,W/m^2$ on
`r strftime(ST_daily[which.max(GLB_diff.max), Date], "%d\\ %B %Y")`.
The relative stronger CE event was 
$`r round(100*ST_daily[which.max(GLB_ench.max), GLB_ench.max],1)`\,\%$ above the 
clear sky threshold, on 
`r strftime(ST_daily[which.max(GLB_ench.max), Date], "%d\\ %B %Y")`.

@@

We computed the daily trend of the mean OIR of CE
(Figure\nobreakspace{}\ref{fig:CEmeanDaily}), using a first-order autoregressive
model with lag of 1 day, using the 'maximum likelihood' fitting method [@Gardner1980;
@Jones1980] by implementing the function 'arima' from the library 'stats' of the R
programming language [@RCT2023]. The trends are reported together with the $2\sigma$
error.  We observe an increase of
$`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate], 3)`\pm
`r round(2 * dailyCE[var == "GLB_diff.mean", Tmod_Std..Error], 3)`\,W/m^2/y$
on the mean OIR.

```{r CEmeanDaily, echo=FALSE, fig.cap="Daily mean values and trend of the CE over irradiance."}
knitr::include_graphics("../images/P_daily_trend-1.png")
```

Although, the previous result is closer to the raw data, we preferred to present the
annual statistics, that give a more clear picture about the long term CE trends.
Hence, we calculated the annual values from the one-minute measurements.  The trend of
OIR is
$`r round(yearlyCE[var == "GLB_diff.mean", slope], 2)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 2)`\,W/m^2/y$
(Figure\nobreakspace{}\ref{fig:P-energy-mean}),
but this value alone is not very useful due the intrinsic high variability of this
metric.

@@

```{r P-energy-mean, echo=FALSE, fig.cap="Trends of the mean OIR per CE."}
knitr::include_graphics("../images/P_energy-7.png")
```

A better indicator of changes on the characteristic of CE would be the number of CE
occurrences and the total energy of the CE over irradiance. The annual number of CE
occurrences, shows a steady increase of
$`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/y$
(Figure\nobreakspace{}\ref{fig:P-energy-N}).
We have to note that the energy related to the CE events can not be directly linked
with the total energy balance on the atmosphere. The net sun radiation of the region
is not increased, but rather redistributed through the CE. Although, the
instantaneous values, can exceed the equivalent clear sky irradiance to a
considerable level.

@@

Subsequently, the mean annual increase of energy due to CE events is
$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,kJ/y$
(Figure\ \ref{fig:P-energy-sum}), witch follows the trend of the number of
occurrences.

@@

```{r P-energy-median, echo=FALSE, fig.cap="Trend of the yearly median over irradiance due to CE over irradiance"}
knitr::include_graphics("../images/P_energy-8.png")
```

@@

## Climatology

Another interesting aspect of the CE cases, is their seasonal cycle. In
Figure\nobreakspace{}\ref{fig:relative-month-occurancies}, we have the box plot
(whisker plot), where the values have been normalized by the highest median value,
that occurs in May.  Although the number of occurrences has a wide spread throughout
the study period, the most active period of CE occurrences is during May and June.
During the Winter (December -- February) the CE cases are about $25\,\%$ of the maximum.
The rest of the months the occurrences ramp between the maximum and minimum.

@@

>>>>

header-includes:
  - \usepackage{caption}
  - \usepackage{placeins}
  - \captionsetup{font=small}

@@

To give a better understanding of the CE identification procedure, we provide an
example of the CE identification for a selected day in the Appendix
(Figure\nobreakspace{}\ref{fig:example-day}), where the use of the reference and the
threshold are shown, along with the relevant measurements.  Similar we provide an
example plot of one year data, where the relation of the GHI and clear sky reference
is shown, along with the OIR intensity also in the Appendix
Figure\nobreakspace{}\ref{fig:example-year}.

@@

Our dataset, after the data selection processing, consists of
`r ST_total$wattGLB.N` records of GHI, of which
$`r round(100*ST_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ are CE events and
$`r round(100*ST_extreme_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ are ECE events.
The highest GHI recorder was 
$`r round(ST_daily[which.max(wattGLB.max), wattGLB.max],1)`\,W/m^2$
on `r strftime(ST_daily[which.max(wattGLB.max), Date], "%d\\ %B %Y")`.
The absolute stronger CE event had an OIR of 
$`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 2)`\,W/m^2$ on
`r strftime(ST_daily[which.max(GLB_diff.max), Date], "%d\\ %B %Y")`.
The relative stronger CE event was 
$`r round(100*ST_daily[which.max(GLB_ench.max), GLB_ench.max],1)`\,\%$ above the 
clear sky threshold, on 
`r strftime(ST_daily[which.max(GLB_ench.max), Date], "%d\\ %B %Y")`.

@@

We computed the daily trend of the mean OIR of CE <!--
(Figure\nobreakspace{}\ref{fig:CEmeanDaily}), --> using a first-order autoregressive
model with a lag of one day, with the 'maximum likelihood' fitting method
[@Gardner1980; @Jones1980] by implementing the function 'arima' from the library
'stats' of the R programming language [@RCT2023]. The trends are reported together
with the $2\sigma$ error.  We observed a negligible change of
$`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate], 3)`\pm
`r round(2 * dailyCE[var == "GLB_diff.mean", Tmod_Std..Error], 3)`\,W/m^2/y$
on the mean OIR.
<!-- ```{r CEmeanDaily, echo=FALSE, fig.cap="Daily mean values and trend of the CE over irradiance."} -->
<!-- knitr::include_graphics("../images/P_daily_trend-1.png") -->
<!-- ``` -->
Although, the previous result is closer to the raw data, we preferred to present the
annual statistics, that give a more clear picture about the long term CE trends.
Hence, we calculated the annual values from the one-minute measurements.  Despite the
very weak statistical significance of the mean OIR trend, the annual number of CE
occurrences shows a steady increase of
$`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/y$
(Figure\nobreakspace{}\ref{fig:P-energy-N}).
Subsequently, the mean annual energy of the CE events is increasing with a rate of
$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,kJ/y$
(Figure\ \ref{fig:P-energy-sum}), witch follows the trend of the number of
occurrences.  We have to note that the energy related to the CE events can not be
directly linked with the total energy balance of the atmosphere. The net solar
radiation of the region is not increased, but rather redistributed through the CE
events.  This also is depicted by the "instantaneous" values of irradiance (average
over one minute), that can exceed the equivalent clear sky irradiance to a
considerable level.

<!-- $`r round(yearlyCE[var == "GLB_diff.mean", slope], 2)`\pm -->
<!-- `r round(2 * yearlyCE[var == "GLB_diff.mean", slope.sd], 2)`\,W/m^2/y$ -->
<!-- (Figure\nobreakspace{}\ref{fig:P-energy-mean}), -->
<!-- but this value alone is not very useful due the intrinsic high variability of this -->
<!-- metric. -->

@@

<!-- ```{r P-energy-mean, echo=FALSE, fig.cap="Trends of the mean OIR per CE."} -->
<!-- knitr::include_graphics("../images/P_energy-7.png") -->
<!-- ``` -->

@@

@@

<!-- ```{r P-energy-median, echo=FALSE, fig.cap="Trend of the yearly median over irradiance due to CE over irradiance"} -->
<!-- knitr::include_graphics("../images/P_energy-8.png") -->
<!-- ``` -->

@@

## CE Climatology

Another interesting aspect of the CE cases, is their seasonal cycle. In
Figure\nobreakspace{}\ref{fig:relative-month-occurancies}, we have the box plot
(whisker plot), where the values have been normalized by the highest median value,
that occurs on June.  Although the number of occurrences has a wide spread throughout
the study period, the most active period of CE occurrences is during May and June.
During the Winter (December -- February) the CE cases are about $25\,\%$ of the maximum.
For the rest months the occurrences gradually ramp between the maximum and minimum.

@@

```{r example-day, echo=FALSE, fig.cap="Example of cloud indentification data for 2019-07-11. Where are denoted with red circles all the detected CE events, the cloud intearaction with the GHI (blue crosses), and the thesholds of CE and the threshold of ECE events with red and black line respectively."}
knitr::include_graphics("../images/example_days-18.png")
```

```{r example-year, echo=FALSE, fig.cap="Example of the relation of the measured GHI versus the reference clear sky irradiance for the year 2005, where the intesity of the detected over irradianse (OIR) is color coded."}
knitr::include_graphics("../images/example_years-13.png")
```

### 2024-05-23 article/article.tex
Commit 2024-05-23 10:10

We computed the daily trend of the mean OIR of CE using a first-order
autoregressive model with lag of 1 day, with the `maximum likelihood'
fitting method \citep{Gardner1980, Jones1980} by implementing the
function `arima' from the library `stats' of the R programming language
\citep{RCT2023}. The trends are reported together with the \(2\sigma\)
error. We observe an negligible change of \(0.087\pm 0.08\,W/m^2/y\) on
the mean OIR.

Although, the previous result is closer to the raw data, we preferred to
present the annual statistics, that give a more clear picture about the
long term CE trends. Hence, we calculated the annual values from the
one-minute measurements. Although, the trend of the mean OIR has very
weak statistical significance, the annual number of CE occurrences,
shows a steady increase of \(45.6\pm 21.9\,\text{cases}/y\)
(Figure\nobreakspace{}\ref{fig:P-energy-N}). We have to note that the
energy related to the CE events can not be directly linked with the
total energy balance on the atmosphere. The net solar radiation of the
region is not increased, but rather redistributed through the CE events.
Resulting, instantaneous values, that can exceed the equivalent clear
sky irradiance to a considerable level.

@@

Subsequently, the mean annual increase of energy due to CE events is
\(116.9\pm 67.8\,kJ/y\) (Figure~\ref{fig:P-energy-sum}), witch follows
the trend of the number of occurrences.

@@

\hypertarget{climatology}{%
\subsection{Climatology}\label{climatology}}

Another interesting aspect of the CE cases, is their seasonal cycle. In
Figure\nobreakspace{}\ref{fig:relative-month-occurancies}, we have the
box plot (whisker plot), where the values have been normalized by the
highest median value, that occurs in May. Although the number of
occurrences has a wide spread throughout the study period, the most
active period of CE occurrences is during May and June. During the
Winter (December -- February) the CE cases are about \(25\,\%\) of the
maximum. The rest of the months the occurrences ramp between the maximum
and minimum.

>>>>

We computed the daily trend of the mean OIR of CE using a first-order
autoregressive model with a lag of one day, with the `maximum
likelihood' fitting method \citep{Gardner1980, Jones1980} by
implementing the function `arima' from the library `stats' of the R
programming language \citep{RCT2023}. The trends are reported together
with the \(2\sigma\) error. We observed a negligible change of
\(0.087\pm 0.08\,W/m^2/y\) on the mean OIR. Although, the previous
result is closer to the raw data, we preferred to present the annual
statistics, that give a more clear picture about the long term CE
trends. Hence, we calculated the annual values from the one-minute
measurements. Despite the very weak statistical significance of the mean
OIR trend, the annual number of CE occurrences shows a steady increase
of \(45.6\pm 21.9\,\text{cases}/y\)
(Figure\nobreakspace{}\ref{fig:P-energy-N}). Subsequently, the mean
annual energy of the CE events is increasing with a rate of
\(116.9\pm 67.8\,kJ/y\) (Figure~\ref{fig:P-energy-sum}), witch follows
the trend of the number of occurrences. We have to note that the energy
related to the CE events can not be directly linked with the total
energy balance of the atmosphere. The net solar radiation of the region
is not increased, but rather redistributed through the CE events. This
also is depicted by the ``instantaneous'' values of irradiance (average
over one minute), that can exceed the equivalent clear sky irradiance to
a considerable level.

@@

@@

\hypertarget{ce-climatology}{%
\subsection{CE Climatology}\label{ce-climatology}}

Another interesting aspect of the CE cases, is their seasonal cycle. In
Figure\nobreakspace{}\ref{fig:relative-month-occurancies}, we have the
box plot (whisker plot), where the values have been normalized by the
highest median value, that occurs on June. Although the number of
occurrences has a wide spread throughout the study period, the most
active period of CE occurrences is during May and June. During the
Winter (December -- February) the CE cases are about \(25\,\%\) of the
maximum. For the rest months the occurrences gradually ramp between the
maximum and minimum.
